---
title: "Harmonization"
author: "Pedro Salguero"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_depth: 4
  pdf_document:
    toc: yes
    toc_depth: 4
editor_options:
  chunk_output_type: inline
params:
  HP_output: 
    label: "Harmonization Problems Output: (should be a RData)"
    value: "D:/Pedro/Mega/Doctorado/Otros proyectos/COVID19/results/1.Harmonization_Problems/harmonization_problems.output.RData"
    input: file
  excel_cat1: 
    label: "Path of Dataset 2 vs Reference Excel File: (should be a .xlsx file with the information complete by yourself)"
    value: "D:/Pedro/Mega/Doctorado/Otros proyectos/COVID19/results/1.Harmonization_Problems/Humanitas2Calabria_fixed.xlsx"
    input: file
  excel_cat2: 
    label: "Path of Dataset 3 vs Reference Excel File: (should be a .xlsx file with the information complete by yourself)"
    value: "D:/Pedro/Mega/Doctorado/Otros proyectos/COVID19/results/1.Harmonization_Problems/Monza2Calabria_fixed.xlsx"
    input: file
  excel_cat3: 
    label: "Path of Dataset 4 vs Reference Excel File: (should be a .xlsx file with the information complete by yourself)"
    value: "D:/Pedro/Mega/Doctorado/Otros proyectos/COVID19/results/1.Harmonization_Problems/Spain2Calabria_fixed.xlsx"
    input: file
  excel_cat4:
    label: "Path of Dataset 5 vs Reference Excel File: (should be a .xlsx file with the information complete by yourself)"
    value: "NA"
    input: file
  NAME_MERGE1:
    label: "Name for merge database:"
    value: "Italian"
    input: text
  NAME_DDBB1:
    label: "Which databases should be joined? (use exact names appear in the Excel template separated by spaces)"
    value: "Calabria Humanitas Monza"
    input: text
  NAME_MERGE2:
    label: "Name for merge database:"
    value: "European"
    input: text
  NAME_DDBB2:
    label: "Which databases should be joined? (use exact names appear in the Excel template separated by spaces)"
    value: "Calabria Humanitas Monza Spain"
    input: text
  NAME_MERGE3:
    label: "Name for merge database:"
    value: ""
    input: text
  NAME_DDBB3:
    label: "Which databases should be joined? (use exact names appear in the Excel template separated by spaces)"
    value: ""
    input: text
  MERGE_METHOD: 
    label: "Do you want to merge the databases using only the variables in common? If not, all variables from reference will be keeped (not recomended)."
    value: TRUE
  FUNCTIONS_PATH: 
    label: "Folder path with all function scripts: (select any file)"
    value: "D:/Pedro/Mega/Doctorado/Otros proyectos/COVID19/scripts/functions/1.Functions.R"
    input: file
  OUTPUT: 
    label: "Output path: (a folder with the results will be create inside this folder)"
    value: "D:/Pedro/Mega/Doctorado/Otros proyectos/COVID19/results/"
    input: text
  PARALLEL: 
    label: "Do you want to run the script with multicore option?"
    value: TRUE
---

```{r new max size, message=F, eval=F, include=F, results='hide'}
#If your file is greater than 5Mb, update the maximum size
new_size = 30 #Mb
options(shiny.maxRequestSize=new_size*1024^2)
rm(new_size)
```

```{r setup, message=F, include=F, results='hide'}
# Chunk options - ALREADY IN GGPLOT2 SOURCE
knitr::opts_chunk$set(
 echo=F,
 warning=F,
 message=F, 
 error = F
)

dpi = 300

knitr::opts_chunk$set(
 dpi=dpi, 
 fig.retina=1, 
 fig.width=1440/dpi, #4:3 FHD
 fig.height=1080/dpi, 
 out.width="100%"
)

rm(dpi)
```

```{r functions}
#Load REPORT functions
loadReportFunctions <- function(path){
  file <- paste0(path,"0.ReportFunctions.R")
  source(file, echo = F)
}

#Load 1.Functions functions
loadFunctions_1 <- function(path){
  file <- paste0(path,"1.Functions.R")
  source(file, echo = F)
}

#Load 2.Functions functions
loadFunctions_2 <- function(path){
  file <- paste0(path,"2.Functions.R")
  source(file, echo = F)
}

#Get CSS Style
getCSS_file <- function(path){
  files <- list.files(path)
  file <- files[which(endsWith(files, ".css"))]
  return(paste0(path, file))
}

#Load ggplot theme
loadGgplotTheme <- function(path){
  file <- paste0(path,"ggplot_theme.R")
  source(file, echo = F)
}

loadFunctions <- function(path){
  loadReportFunctions(path)
  loadFunctions_1(path)
  loadFunctions_2(path)
  loadGgplotTheme(path)
  rmarkdown::html_document(css = getCSS_file(path))
}
```

```{r libraries}
library(readxl, quietly = T)
library(openxlsx, quietly = T)
library(future, quietly = T)
library(VennDiagram, quietly = T)
library(UpSetR, quietly = T)
library(furrr, quietly = T)
library(ggplot2, quietly = T)
library(RColorConesa, quietly = T)
library(kableExtra, quietly = T)
library(stringr, quietly = T)
library(dplyr, quietly = T)
library(grid, quietly = T)
library(RColorConesa, quietly = T)
library(stringdist, quietly = T)
```

<!-- 
#########
# INPUT #
#########
-->

```{r load all functions, include=F}
#It will fail in other OS
if(endsWith(params$FUNCTIONS_PATH, "/")){
  loadFunctions(params$FUNCTIONS_PATH)
}else{
  index <- gregexpr("/", params$FUNCTIONS_PATH)[[1]]
  index <- index[length(index)]
  fpath <- substr(params$FUNCTIONS_PATH, 1, index)
  loadFunctions(fpath)
}
```

<!-- 
##########
# 1.DATA #
##########
-->

```{r readData - 1}
if(endsWith(params$HP_output, ".RData") | endsWith(params$HP_output, ".RDS")){
  load(params$HP_output)
}else{
  stop("Harmonization Problems output must be the .RData object (called harmonization_problems.output).")
}
```

```{r FOLDER for save results}
FOLDER <- paste0(ifelse(endsWith(params$OUTPUT, "/"),params$OUTPUT,paste0(params$OUTPUT, "/")),"2.Harmonization/")
dir.create(FOLDER)
```

```{r NAMES_REFERENCE}
PARALLEL = as.logical(params$PARALLEL)
```

<!-- 
########################
# READ CATEGORY EXCELS #
########################
-->

```{r update categories}
name_files <- c(params$excel_cat1, params$excel_cat2, params$excel_cat3, params$excel_cat4)
name_files <- name_files[!name_files=="NA"]

if(PARALLEL){
  n_cores <- max(future::availableCores() - 1, 1)
  
  if(.Platform$OS.type == "unix") {
    future::plan("multicore", workers = min(length(name_files), n_cores))
  }else{
    future::plan("multisession", workers = min(length(name_files), n_cores))
  }
  
  lst_excel <- furrr::future_map(name_files, ~openxlsx::read.xlsx(., colNames = F, rowNames = F))
  future::plan("sequential")
}else{
  lst_excel <- purrr::map(name_files, ~openxlsx::read.xlsx(., colNames = F, rowNames = F))
}

names(lst_excel) <- NAMES_NOT_REFERENCE

if(PARALLEL){
  n_cores <- max(future::availableCores() - 1, 1)
  
  if(.Platform$OS.type == "unix") {
    future::plan("multicore", workers = min(length(LST_DATA[NAMES_NOT_REFERENCE]), n_cores))
  }else{
    future::plan("multisession", workers = min(length(LST_DATA[NAMES_NOT_REFERENCE]), n_cores))
  }
  
  lst_fixed <- furrr::future_map2(.x = LST_DATA[NAMES_NOT_REFERENCE], 
                         .y = lst_excel, 
                         ~updateFactorExcel(.x, .y))
  future::plan("sequential")
}else{
  lst_fixed <- purrr::map2(.x = LST_DATA[NAMES_NOT_REFERENCE], 
                         .y = lst_excel, 
                         ~updateFactorExcel(.x, .y))
}

lst_fixed[[NAMES_REFERENCE]] <- LST_DATA[[NAMES_REFERENCE]]
lst_fixed <- lst_fixed[c(4,1,2,3)]

rm(name_files, lst_excel)
```

<!-- 
########################################
# Update REFERENCE with new CATEGORIES #
########################################
-->

## Reference Variables with new Categories/Levels {.tabset .tabset-fade}

It has been added new categories for the following variables:

```{r update NAMES_REFERENCE levels}
cn_factor <- getFactorNames(lst_fixed[[NAMES_REFERENCE]])

var_updated <- NULL

for(cn in cn_factor){
  lvl_ref <- levels(lst_fixed[[NAMES_REFERENCE]][,cn])
  
  lvl_others <- NULL
  for(db in NAMES_NOT_REFERENCE){
    if(cn %in% colnames(lst_fixed[[db]])){
      lvl_others <- c(lvl_others, levels(lst_fixed[[db]][,cn]))
    }
  }
  lvl_others <- unique(lvl_others)
  
  if(all(lvl_others %in% lvl_ref)){
    next
  }else{
    lvl_new <- lvl_others[!lvl_others %in% lvl_ref]
  }
  
  lst_fixed[[NAMES_REFERENCE]] <- addFactors(lst_fixed[[NAMES_REFERENCE]], cn, lvl_new)
  var_updated <- c(var_updated, cn)
}

df_var_updated <- getVarDescDF(VAR_DESCRIPTION, var_updated)
RES_VAR_UPDATED <- list("New Categories" = df_var_updated)

rm(cn_factor, df_var_updated)
```

```{r plot info7, results='asis'}
printDFInHTML_ByTabs(lst_names = names(RES_VAR_UPDATED), lst_dataframes = RES_VAR_UPDATED)
rm(RES_VAR_UPDATED)
```

<!-- ################# -->
<!-- # JOIN DATASETS # -->
<!-- ################# -->

## Databases have been merged {.tabset .tabset-fade}

```{r names to merge}
HOWTOMERGE <- list(strsplit(params$NAME_DDBB1, " ")[[1]], strsplit(params$NAME_DDBB2, " ")[[1]], strsplit(params$NAME_DDBB3, " ")[[1]])

#NAMES MUST BE IN NAMES_DDBB
empty <- NULL
for(ddbb_m in 1:length(HOWTOMERGE)){
  empty <- c(empty, length(HOWTOMERGE[[ddbb_m]])==0)
  if(!empty & !all(HOWTOMERGE[[ddbb_m]] %in% NAMES_DDBB)){
    stop(paste0("Names of Databases to merge must be some of the follows: ", NAMES_DDBB))
  }
}

HOWTOMERGE[empty] <- NULL

NAMES_MERGE <- c(params$NAME_MERGE1, params$NAME_MERGE2, params$NAME_MERGE3)

empty = nchar(NAMES_MERGE)==0
NAMES_MERGE <- NAMES_MERGE[!empty]

if(length(NAMES_MERGE) != length(HOWTOMERGE)){
  stop(paste0("You provided a total of ", length(NAMES_MERGE), " (", paste0(NAMES_MERGE, collapse = ", "), ") names and ", length(HOWTOMERGE), " ways of merge."))
}

names(HOWTOMERGE) <- NAMES_MERGE
```

The new databases with all the information merged are called: `r NAMES_MERGE`.

```{r}
merged_method <- params$MERGE_METHOD
```

`r ifelse(merged_method, "The databases are merged using the common variables between all sources.", "The databases are merged using all the variables the reference database has. If a new database does not have those variables, a new column will be created with all the values as missing values.")`

```{r joinDataSets}
if(PARALLEL){
  n_cores <- max(future::availableCores() - 1, 1)
  
  if(.Platform$OS.type == "unix") {
    future::plan("multicore", workers = min(length(lst_fixed), n_cores))
  }else{
    future::plan("multisession", workers = min(length(lst_fixed), n_cores))
  }
  
  lst_namevars <- furrr::future_map(lst_fixed, ~colnames(.))
  future::plan("sequential")
}else{
  lst_namevars <- purrr::map(lst_fixed, ~colnames(.))
}

#intersect 1:2
intersect_vars <- list()
for(h in names(HOWTOMERGE)){
  intersect_vars[[h]] <- intersect(lst_namevars[[HOWTOMERGE[[h]][[1]]]], lst_namevars[[HOWTOMERGE[[h]][[2]]]])
  if(length(HOWTOMERGE[[h]])>2){
    for(i in 3:length(HOWTOMERGE[[h]])){
      intersect_vars[[h]] <- intersect(intersect_vars[[h]], lst_namevars[[HOWTOMERGE[[h]][[i]]]])
    }
  }
}

lst_merge <- list()
for(db in names(HOWTOMERGE)){
  aux <- NULL
  for(data_name in names(lst_fixed)){
    if(data_name %in% HOWTOMERGE[[db]]){
      if(merged_method){
        aux <- dplyr::bind_rows(aux, lst_fixed[[data_name]][,intersect_vars[[db]]]) #original datasets merge
      }else{
        aux <- dplyr::bind_rows(aux, lst_fixed[[data_name]]) #original datasets merge
      }
    }
  }
  lst_merge[[db]] <- aux
}

rm(aux, HOWTOMERGE)

####
# NOW, NAMES_REFERENCES KEEP ALL COLUMNS, if merged_method == F
# and KEEP INTERSECTION if merged_method = T
####
```

A new variable call "SOURCE" has been created to identify from which database are each sample.

```{r create SOURCE variable to indentify from which ddbb come each patient}
VAR_DDBB <- "SOURCE"

for(db in names(lst_merge)){
  lst_merge[[db]][,VAR_DDBB] <- NA
  data <- lst_merge[[db]]
  for(db_name in names(lst_fixed)){
    index <- which(rownames(data) %in% rownames(lst_fixed[[db_name]]))
    data$SOURCE[index] <- db_name
    lst_merge[[db]] <- data
  }
  lst_merge[[db]][,VAR_DDBB] <- as.factor(lst_merge[[db]][,VAR_DDBB])
}

#add variable to list
VAR_DESCRIPTION <- addVarInfo(VAR_DESCRIPTION, VAR_DDBB, "SOURCE to identify original database", "OTHER")

rm(data)
```

```{r new structe}
LST_DATA <- lst_fixed
LST_DATA_MERGE <- lst_merge
LST_DATA_ALL <- append(LST_DATA, LST_DATA_MERGE)

rm(lst_fixed, lst_merge)
```

## Drop unused levels {.tabset .tabset-fade}

After merged, we can removed unused levels for categorical variables. Categorical variables with just one factor or category will be detected and removed because do not provide useful information.

```{r drop unused factor levels}
#Drops unused factor levels
if(PARALLEL){
  n_cores <- max(future::availableCores() - 1, 1)
  
  if(.Platform$OS.type == "unix") {
    future::plan("multicore", workers = min(length(LST_DATA_ALL), n_cores))
  }else{
    future::plan("multisession", workers = min(length(LST_DATA_ALL), n_cores))
  }
  
  LST_DATA_ALL <- furrr::future_map(LST_DATA_ALL, ~dropLevelsAllColumns(data = .))
  LST_DATA <- furrr::future_map(LST_DATA, ~dropLevelsAllColumns(data = .))
  LST_DATA_MERGE <- furrr::future_map(LST_DATA_MERGE, ~dropLevelsAllColumns(data = .))
  future::plan("sequential")
}else{
  LST_DATA_ALL <- purrr::map(LST_DATA_ALL, ~dropLevelsAllColumns(data = .))
  LST_DATA <- purrr::map(LST_DATA, ~dropLevelsAllColumns(data = .))
  LST_DATA_MERGE <- purrr::map(LST_DATA_MERGE, ~dropLevelsAllColumns(data = .))
}
```

## Basic Information - Merged Data {.tabset .tabset-fade}

```{r basic information}
if(PARALLEL){
  n_cores <- max(future::availableCores() - 1, 1)
  
  if(.Platform$OS.type == "unix") {
    future::plan("multicore", workers = min(length(LST_DATA_ALL), n_cores))
  }else{
    future::plan("multisession", workers = min(length(LST_DATA_ALL), n_cores))
  }
  
  RES_BASIC_INFORMATION <- furrr::future_map(LST_DATA_ALL, ~info_dimensions(data = .))
  future::plan("sequential")
}else{
  RES_BASIC_INFORMATION <- purrr::map(LST_DATA_ALL, ~info_dimensions(data = .))
}
```

```{r plot info - basic information, results='asis'}
printDFInHTML_ByTabs(RES_BASIC_INFORMATION, RES_BASIC_INFORMATION)
```

## Save Process {.tabset .tabset-fade}

Databases are saved in .RData and .xlsx format with their new colnames. Excel format does not save the same R class for each variable. We recommend to work with .RData files in case you want to do your own study.

```{r save data, include=F}
library(openxlsx)
if(PARALLEL){
  n_cores <- max(future::availableCores() - 1, 1)
  
  if(.Platform$OS.type == "unix") {
    future::plan("multicore", workers = min(length(LST_DATA_ALL), n_cores))
  }else{
    future::plan("multisession", workers = min(length(LST_DATA_ALL), n_cores))
  }
  
  furrr::future_map2(.x = LST_DATA_ALL, .y = names(LST_DATA_ALL), ~write.xlsx(.x, file = paste0(FOLDER,.y,'.xlsx'), overwrite = T))
  furrr::future_map2(.x = LST_DATA_ALL, .y = names(LST_DATA_ALL), ~save(.x, file = paste0(FOLDER,.y,'.RData')))
  future::plan("sequential")
}else{
  purrr::map2(.x = LST_DATA_ALL, .y = names(LST_DATA_ALL), ~write.xlsx(.x, file = paste0(FOLDER,.y,'.xlsx'), overwrite = T))
  purrr::map2(.x = LST_DATA_ALL, .y = names(LST_DATA_ALL), ~save(.x, file = paste0(FOLDER,.y,'.RData')))
}

rm(params)
rm(list = ls.str(mode = 'numeric')[str_detect(ls.str(mode = "numeric"),"[[:lower:]]")])
rm(list = ls.str(mode = 'character')[str_detect(ls.str(mode = "character"),"[[:lower:]]")])
rm(list = ls.str(mode = 'logical')[str_detect(ls.str(mode = "logical"),"[[:lower:]]")])
rm(list = ls.str(mode = 'NULL')[str_detect(ls.str(mode = "NULL"),"[[:lower:]]")])
rm(list = ls.str(mode = 'function'))
```

```{r saveData workspace, results="hide", include=F}
save.image(paste0(FOLDER,"harmonization.output.RData"))
```
